L’évolution des technologies et leurs usages ont fait exploser la quantité de données générées. Selon IBM, 2.5 milliard de gigabytes (GB) de données a été générée tout les jours de l'année 2012. De plus, cette quantité de données, double tous les deux ans. Cependant, seules 0,05\% de ces données sont analysées.\\

L’exploration ou la fouille de données (``data mining'') consiste à en extraire des informations utiles, et ceci peut s’avérer très fructueux. La question principale qui se pose est de savoir comment utiliser intelligemment cette immense masse de données pour en tirer une plus-value ?\\


Bitbond is a startup offering to everyone the possibility to borrow money in affordable terms or to lend money with profitable interest rate. Bitbond operates thanks to a peer-to-peer Bitcoin lending platform. Thanks to their idea, small businesses get access to affordable loans while lenders earn profitable interest rates. Since Bitbond works exclusively with the digital currency Bitcoin, neither the borrower nor the lender need a bank account to participate in our global loan market.\\
Bitbond's mission is to make investing and financing globally accessible.\\

The main purpose of this project is to use the data of Bitbond (which are accessible to everyone) to analyse it and follow a machine learning procedure to identify the financial risks.\\

Anyone who wish to get a loan must satisfy some requirements :
\begin{enumerate}
    \item He must register on the platform ;
    \item He must inform about his name, his gender, his date of birth and his country of citizenship ;
    \item He must inform about his phone, his address and if he had moved within the last 3 months ;
    \item He must inform about his employment (self-employed, salaried, retired, etc.) ;
    \item He must inform about different account he may have (ebay, paypal, facebook, etc.) to show his healthy activity ;
\end{enumerate}
Then, Bitbond uses all those informations to compute indicators. In fact, those informations allow Bitbond to assess the ability of the borrower to pay back a loan : the creditworthiness (represents by a letter).\\
For this indicator, Bitbond asks for credit informations and compute a score. This score conducts the rating for the creditworthiness, as well as the type of employment, the connection of the personal PayPal account, the eBay feedback score, the country of residence and the payment history of bitcoin loans.\\